Placeholder for article 3

### 2025-01-08 analysis/paper/paper.qmd
Width, length and weight boxplots + ggarrange

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(janitor)

@@

```{r}
#| label: stats

# Solutrean statistics
solu_stats <- solutrean_dataset %>% 
  filter(RMTYPE != "INDET") %>%
   mutate(CLASS = case_when(
    CLASS == "Thinning flake" ~ "ThinningFlake",
    CLASS == "ElongBlank" ~ "ElongatedProd",
    CLASS == "FlakeFrag" | CLASS == "ElongBlankFrag" ~ "BlankFrag",
    CLASS == "Retouched piece" ~ "RetouchedPiece",
    TRUE ~ CLASS)) %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS))
# For flakes (complete)
solu_stats_blanks <- solu_stats %>% 
  filter(CLASS %in% c("Flake", "ElongatedProd")) %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For Thinning flakes
solu_stats_thin <- solu_stats %>% 
  filter(CLASS == "ThinningFlake") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For cores
solu_stats_cores <- solu_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For retouched
solu_stats_retouched <- solu_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# Proto-solutrean statistics ds prep
proto_stats <- phase_dataset %>% 
  filter(Level %in% c("4E", "4E/5")) %>% 
  filter(RMTYPE != "INDET") %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS)) %>%
  mutate(elong = MAXWIDTH*2-LENGTH) %>%
  mutate(CLASS = case_when(
    CLASS == "Blank" & elong > 0 ~ "Flake",
    CLASS == "Blank" & elong <= 0 ~ "ElongatedProd",
    TRUE ~ CLASS))

# For blanks (complete)
proto_stats_blanks <- proto_stats %>% 
  filter(CLASS == "Flake") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# For cores
proto_stats_cores <- proto_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# For retouched
proto_stats_retouched <- proto_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# Gravettian statistics ds prep
grav_stats <- phase_dataset %>%
  filter(Level %in% c(6, 7)) %>%
  filter(RMTYPE != "INDET") %>%
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS))

# For blanks (complete)
grav_stats_blanks <- grav_stats %>% 
  filter(CLASS == "Blank") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# For cores
grav_stats_cores <- grav_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# For retouched
grav_stats_retouch <- grav_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

grav_stats %>%
  filter(CLASS %in% c("Blank", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Blank", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

grav_stats %>%
  filter(CLASS %in% c("Blank", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Blank", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

>>>>

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(janitor)
library(ggpubr)

@@

```{r}
#| label: stats-setup

# Solutrean statistics
# DS preparation
solutrean_stats <- solutrean_dataset %>% 
  filter(RMTYPE != "INDET") %>%
   mutate(CLASS = case_when(
    CLASS == "Thinning flake" ~ "ThinningFlake",
    CLASS == "ElongBlank" ~ "ElongatedProd",
    CLASS == "FlakeFrag" | CLASS == "ElongBlankFrag" ~ "BlankFrag",
    CLASS == "Retouched piece" ~ "RetouchedPiece",
    TRUE ~ CLASS)) %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS))

# Boxplot for individual measurements
# Length
solutrean_stats_length <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
solutrean_stats_weight <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Width
solutrean_stats_width <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

# Tables with individual class. For supplementary information if necessary
# For flakes (complete)
solutrean_stats_blanks <- solutrean_stats %>% 
  filter(CLASS %in% c("Flake", "ElongatedProd")) %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For cores
solutrean_stats_cores <- solutrean_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For retouched
solutrean_stats_retouched <- solutrean_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# Proto-Solutrean statistics
# DS prep
proto_stats <- phase_dataset %>% 
  filter(Level %in% c("4E", "4E/5")) %>% 
  filter(RMTYPE != "INDET") %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS)) %>%
  mutate(elong = MAXWIDTH*2-LENGTH) %>%
  mutate(CLASS = case_when(
    CLASS == "Blank" & elong > 0 ~ "Flake", # QUESTION: do I keep flakes and elong separate or join into blanks?
    CLASS == "Blank" & elong <= 0 ~ "ElongatedProd",
    TRUE ~ CLASS))

# Boxplots
# Width
proto_stats_width <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Length
proto_stats_length <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
proto_stats_weight <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

# Tables with individual class. For supplementary information if necessary
# For flakes (complete)
proto_stats_flakes <- proto_stats %>% 
  filter(CLASS == "Flake") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For cores
proto_stats_cores <- proto_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For retouched
proto_stats_retouched <- proto_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

# Gravettian statistics
# DS prep
gravettian_stats <- phase_dataset %>%
  filter(Level %in% c(6, 7)) %>%
  filter(RMTYPE != "INDET") %>%
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS)) %>% 
  mutate(elong = MAXWIDTH*2-LENGTH) %>%
  mutate(CLASS = case_when(
    CLASS == "Blank" & elong > 0 ~ "Flake", # QUESTION: do I keep flakes and elong separate or join into blanks?
    CLASS == "Blank" & elong <= 0 ~ "ElongatedProd",
    TRUE ~ CLASS))

# Boxplots
# Width
gravettian_stats_width <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Length
gravettian_stats_length <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(10, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
gravettian_stats_weight <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

# Tables with individual class. For supplementary information if necessary
# For flakes (complete)
gravettian_stats_flakes <- gravettian_stats %>% 
  filter(CLASS == "Blank") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For cores
gravettian_stats_cores <- gravettian_stats %>% 
  filter(CLASS == "Core") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
# For retouched
gravettian_stats_retouch <- gravettian_stats %>% 
  filter(CLASS == "RetouchedPiece") %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

```{r}
#| label: fig-solutrean-boxplots

ggpubr::ggarrange(solutrean_stats_width, solutrean_stats_length, solutrean_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")

```{r}
#| label:  fig-proto-boxplots

ggpubr::ggarrange(proto_stats_width, proto_stats_length, proto_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")

```{r}
#| label: fig-gravettian-boxplots

ggpubr::ggarrange(gravettian_stats_width, gravettian_stats_length, gravettian_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")
